Measuring Bibliometric Coverage of German Law Journals

### 2025-04-23 docs/paper.qmd
Update to the conclusion

First of all, the future of bibliometric analyses should not depend on commercial vendors who sell bibliometric metadata at high costs and with restrictive licenses. As we have shown, open suppliers such as OpenAlex already have a better, but still very limited coverage of the German legal domain. The strategy should be to improve open data repositories and make the data readily available to anyone who wants to do their own analyses.

Second, as OpenAlex's data repository is highly dynamic, it is necessary to continually follow its growth and internal refactoring. The queries from this study need to be repeated in order to document improvements of the coverage of the gold standard across database versions. We hope that publishers will continue to upgrade the quality of the data to CrossRef, from which OpenAlex mainly draws. This, we hope, will improve the bibliometric coverage of legal scholarship in German (and other languages) over time.

>>>>

First of all, there more research on knowledge production in the domain of legal scholarship is badly needed, both in terms of producing data and analyzing it. Regardless of one's opinion of the worth of research evaluation metrics, it is important to be able to empirically observe research output. In particular, it can be very useful for systematically studying the reception history of legal ideas, or for quantitative analyses of the intellectual landscape of legal scholarship today. We also need more studies involving expert knowledge such as that of Gröls/Gröls. We hope for a follow-up study that will allow to update our data.

Second, the future of bibliometric analyses should not have to depend on commercial vendors who sell bibliometric metadata at high costs and with restrictive licenses. As we have shown, open suppliers such as OpenAlex already have a better, but still very limited coverage of the German legal domain. The strategy should be to improve open data repositories and make the data readily available to anyone who wants to do their own analyses. As OpenAlex's data repository is highly dynamic, it is necessary to continually follow its growth and internal refactoring. The queries from this study need to be repeated in order to document improvements of the coverage of the gold standard across database versions. We hope that publishers will continue to upgrade the quality of the data to CrossRef, from which OpenAlex mainly draws. This, we hope, will improve the bibliometric coverage of legal scholarship in German (and other languages) over time.
